---
title: "week5-tut"
author: "Kerui Yang"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
tab <- matrix(c(35,42,63,91,104,65,23,27,50),
              ncol=3,
              byrow=TRUE)
colnames(tab) <- c('Business', 'Engineering', 'others')
rownames(tab) <- c('Yes','No','Unsure')
tab <- as.table(tab)
tab
```

a) what percent of studenst are unsure about whether they go to a graduate shcool?

```{r}
sum(tab)
total = sum(tab)
```

```{r}
total_Yes = sum(tab[1,])
total_No = sum(tab[2,])
total_unsure = sum(tab[3,])
```
```{r}
percent = (total_unsure / total)
percent
```


b) Among engineering students, what percent of them plan to go to a graduate school?

```{r}
total_engineering = sum(tab[,2])
percent = (tab[1,2] / total_engineering)
percent
```
c) Among students who plan to go to a graduate school, what percent of them are not engineering
majors?

```{r}
(tab[1,1] + tab[1,3])/total_Yes

```

d) What percent of students are either business or engineering majors and are not unsure about
whether they go to a graduate school or not?

```{r}
total_unsure = sum(tab[3,])
sum(tab[1:2,1:2]) / total 
```



## Question 3
Consider the experiment of rolling a pair of fair dice.
(a) How many outcomes are in the sample space?
```{r}
6*6
```
(b) What is the probability of rolling a 5 (total of the pair is 5)?

```{r}
sample_space <- expand.grid(Die1 = 1:6, Die2 = 1:6)
sample_space
```
```{r}
success_cases <- subset(sample_space, Die1 + Die2 == 5)
success_cases 
```
```{r}
probability <- nrow(success_cases) / nrow(sample_space)
probability
```

(c) What is the probability of rolling an 8 or greater?
```{r}
success_cases <- subset(sample_space, Die1 + Die2 >= 8)
probability <- nrow(success_cases) / nrow(sample_space)
probability
```


### Quesion 4:


```{r}


```

